---
title: "AVO Plots"
author: "Anna Fryjoff-Hung"
date: "October 6, 2018"
output: html_notebook
---
#### Script for plotting datasets processed from:
- PT, CDEC, Storage Capacity 

*Original Plots created in "AVO_Precip_WSE" script* 


#Load Required Packages
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(rvest)
library(tidyverse)
```

#Load Combined PT/WSE/Storage Dataset
```{r}

```


#Plot Cumulative Precip and Depth (Base R)
```{r}
# https://thepracticalr.wordpress.com/2016/08/30/2-y-axis-plotting/ 

png("figs/depth_precip_cum.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(y$DateTime, y$Depth_cm, type ="l", ylab = "Depth (cm)", main = "Depth vs. Cumulative Precip", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(y$DateTime, y$precip_acc_cm, type ="l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Precip (cm)", side = 4, line = 3)
legend("topleft", c("Depth (cm)", "Precip (cm)"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

dev.off()
```



#Plot Cumulative Annual Precip and Depth (ggplot)
```{r}
p <- ggplot(y, aes(x = DateTime))
  p <- p + geom_line(aes(y = Depth_cm), lty = 1, col = "deepskyblue") #+ coord_cartesian(ylim=c(120, 125))

  # adding the precip, transformed to match roughly the range of the WSE
  p <- p + geom_line(aes(y = precip_acc_cm*7), lty = 3, col = "darkblue")
  p

  # now adding the secondary axis, following the example in the help file ?scale_y_continuous
  # and, very important, reverting the above transformation
  p <- p + scale_y_continuous(sec.axis = sec_axis(~./7, name = "Precipitation (cm)"))

  # modifying colours and theme options
  #p <- p + scale_colour_manual(labels = c("Water Surface Elevation (cm)", "Precipitation (cm)"), values = c("blue","red"))
  p <- p + labs(y = "Depth (cm)",
                x = "Date",
                colour = NULL)
  p <- p + ggtitle("Depth vs. Cumulative Precip")
  p <- p + theme(plot.title = element_text(hjust = 0.5))
  p  <- p + theme(legend.position = c(0.85, 0.85))
  p
  
  ggsave("figs/depth_precip_cum_ggplot.png")
```

#Plot Cumulative Monthly Precip and Depth (ggplot)
```{r}
p <- ggplot(y, aes(x = Day))
  p <- p + geom_line(aes(y = Depth_cm), lty = 1, col = "deepskyblue") #+ coord_cartesian(ylim=c(120, 125))

  # adding the precip, transformed to match roughly the range of the WSE
  p <- p + geom_line(aes(y = precip_acc_cm*7), lty = 3, col = "darkblue")
  p

  # now adding the secondary axis, following the example in the help file ?scale_y_continuous
  # and, very important, reverting the above transformation
  p <- p + scale_y_continuous(sec.axis = sec_axis(~./7, name = "Precipitation (cm)"))

  # modifying colours and theme options
  #p <- p + scale_colour_manual(labels = c("Water Surface Elevation (cm)", "Precipitation (cm)"), values = c("blue","red"))
  p <- p + labs(y = "Depth (cm)",
                x = "Date",
                colour = NULL)
  p <- p + ggtitle("Monthly Depth vs. Cumulative Precip")
  p <- p + theme(plot.title = element_text(hjust = 0.5))
  p  <- p + theme(legend.position = c(0.85, 0.85))
  p <- p + facet_wrap(vars(Year, Month))
  p
  
  ggsave("figs/depth_precip_cum_monthly_ggplot.png")
```

#Plot Precip vs Depth Percent Change
```{r}
#Need to sort out noise in data - aggregate to daily? Only positive values for WSE

png("figs/depth_precip_pctchange.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(y$DateTime, y$precip_pct_chg, type ="l", ylab = "% Change in Precip", main = "%Change Precip vs. Depth", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(y$DateTime, y$depth_pct_chg, type ="p", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("% Change in Depth", side = 4, line = 3)
legend("topright", c("% Change in Precip", "% Change in Depth"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

dev.off()
```

#Plotting Storm Event Precip and Pond Vol Gain
```{r}
png("figs/storms_vol_precip.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(storm_stats$start_date, storm_stats$vol_gain, type ="p", pch = 19, ylab = "Volume (m^3)", main = "Storm Events vs. Pond Volume", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(storm_stats$start_date, storm_stats$precip_mm, type ="p", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Precip (mm)", side = 4, line = 3)
legend("left", inset = 0.01, c("Volume (m^3)", "Precip (mm)"),
       col = c("deepskyblue", "darkblue"), pch = c(19, 1))

dev.off()
```

#Plot precip per day (depth mm x area of catchments) x vol of pond per day for each storm event
```{r}

```

#Plot CDEC sensors during storm events (ex: precip vs. soil moisture)
```{r}

```

#Plot: precip data vs. pond rise - delay in precip at pond vs. weather stations
```{r}

```


#Plot CDEC sensors for field season
```{r}

```

#Plot CDEC cumulative precip for availavle WYs
```{r}

```


