---
title: "AVO Data Processing: Pressure Transducers"
author: "Anna Fryjoff-Hung"
date: "October 6, 2018"
output: html_notebook
---

#Wrangle PT Data for Avocet from 11-6-2017-8-10-2018
- Import individual PT datasets
- Adjust PT depths and calculate WSE
- Combine datasets
- Compare against staff gage recordings 

PT Elevations for Adjusted WSE
3/9/17-7/12/17 = 122.54
- corrected with reference water level: 1.12m
7/13/17-9/29/17 = 121.83
- corrected with reference water level: 1.01m - 7/12 @12:45pm
***11/6/17-8/10/18 = 121.47
- corrected with terrestrial PT

##Load Required Packages
```{r}
#Load Required Packages
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(rvest)
library(readr)
```

##Import and adjust PT datasets 

*Should probably be turned into a function to process other study pond data*
- Would need to designate individual PT elevations for WSE correction 

```{r eval = FALSE}
## if was written with pipes
test <- read_csv("data/20180810_AVOCET_corrected_24.csv")[,1:6] %>%
  set_colnames(c("Order","DateTime","PT_kPa","WaterTemp_c","Baro_kPa","PT_Depth_m")) %>%
  filter(complete.cases(.)) %>%
  filter(PT_Depth_m >= 0.1) %>%
  mutate(Adjusted_PTDepth = PT_Depth_m + 0.05,
         DateTime = mdy_hms(DateTime),
         Adjusted_WSE = Adjusted_PTDepth + 121.472)
```


###Import first half of PT Data 11/6/17-3/11/2018
```{r}
#Import first half of PT Data 11/6/17-3/11/2018
x <- read_csv("data/20180311_AVOCET_corrected_24.csv")[,1:6]
names(x) <- c("Order","DateTime","PT_kPa","WaterTemp_c","Baro_kPa","PT_Depth_m")
#x <- dplyr::rename(x, Order = `#`, DateTime = 2, PT_kPa = 3, WaterTemp_c = 4, Baro_kPa = 5, PT_Depth_m = 6)
x <- x[complete.cases(x),]
x <- x[x$PT_Depth_m >= 0.1, ]
#PT suspended ~5cm above bottom of staff gage - adjust by adding 0.05 to recorded depths
x$Adjusted_PTDepth <- x$PT_Depth_m+0.05
x$DateTime <- mdy_hms(x$DateTime)
#Add PT depths to PT elevation to get water surface elevation of pond 
x$Adjusted_WSE <- x$Adjusted_PTDepth + 121.472
AVO_PThobo_0311_cleaned <- x

```

###Import second half of PT Data 3/11/2018 - 8/10/2018
```{r}
#Import second half of PT Data 3/11/2018 - 8/10/2018
x <- read_csv("data/20180810_AVOCET_corrected_24.csv")[,1:6]
names(x) <- c("Order","DateTime","PT_kPa","WaterTemp_c","Baro_kPa","PT_Depth_m")
#x <- dplyr::rename(x, Order = `#`, DateTime = 2, PT_kPa = 3, WaterTemp_c = 4, Baro_kPa = 5, PT_Depth_m = 6)
x <- x[complete.cases(x),]
x <- x[x$PT_Depth_m >= 0.1, ]
#PT suspended ~5cm above bottom of staff gage - adjust by adding 0.05 to recorded depths
x$Adjusted_PTDepth <- x$PT_Depth_m+0.05
x$DateTime <- mdy_hms(x$DateTime)
#Add PT depths to PT elevation to get water surface elevation of pond 
x$Adjusted_WSE <- x$Adjusted_PTDepth + 121.472
AVO_PThobo_0810_cleaned <- x

```

##Combine Datasets
```{r}
#Combine Datasets

AVO_PTcleaned_1718 <- rbind(AVO_PThobo_0311_cleaned, AVO_PThobo_0810_cleaned)
#write_csv(AVO_PTcleaned_1718,  "output/AVO_PTcleaned_1718.csv")
```

##Plot Combined Dataset
```{r}
ggplot(AVO_PTcleaned_1718, aes(x = DateTime, y = Adjusted_PTDepth))+
  geom_line()
```

##Import PT Visual Check Data
```{r}
##Import PT Visual Check Data
x <- read_csv("data/AVO_PTCheck_1718.csv")
x$DateTime <- mdy_hm(x$DateTime)
AVO_PTfieldcheck_1718 <- x
```

###Join and compare observed vs measured values
```{r}
AVO_PTjoin <- merge(x = AVO_PTfieldcheck_1718, y = AVO_PTcleaned_1718, by = "DateTime", all.x = TRUE)
AVO_PTjoin$Obs_Rec_Diff <- (AVO_PTjoin$Observed_Depth - AVO_PTjoin$Adjusted_PTDepth)
AVO_PTjoin_compare <- AVO_PTjoin
#write_csv(AVO_PTjoin_compare, "output/AVO_PTcompare_1718.csv")
```

