---
title: "AVO Step 1: Bind Datasets"
author: "Anna Fryjoff-Hung"
date: "October 6, 2018"
output: html_notebook
---

#### Description:
stuff this does

- Code based on ___ trial script and ____trial script

# Load Required Packages 
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(rvest)
library(readr)
library(oce)
```


##### Step 1: Load in data 


```{r}
#Read in PT data
PT <- read_csv("output/AVO_PTcleaned_1718.csv") %>% 
  rename(WSE = Adjusted_WSE) %>%
  mutate(WSE = round(WSE, digits = 2))
#Adjust WSE to 2 decimel places.  Staff gage reads at cm level correction


#Read in Precip Data
PCP <- read_csv("output/CDECprecip_edited.csv") %>% 
  rename(DateTime = datetime) %>% 
  mutate(precip_acc_mm = precip_acc_in*25.4)

#Read in Storage Capacity Data
SC <- read_csv("data/AVO_StorageCapacity_1cm.csv") %>% 
  rename(WSE = ELEVATION, VOLm3 = VOLUME, SAm = AREA) %>% 
  mutate(WSE = round(WSE, digits = 2), 
         VOLacft = VOLm3*0.000810714,
         SAac = SAm*0.000247105)

```



##### Step 2: Bind data1 to data2 
because using this column

```{r}
pondflux_15min <- PT %>% 
  inner_join(PCP, by = "DateTime") %>% 
  inner_join(SC, by = "WSE") %>% 
  mutate(PCPacft = precip_event_mm*0.00328084*173.8, PCPacft_acc = cumsum(PCPacft), Date = date(DateTime)) #%>% 
#  write.csv("output/pondflux_15min.csv")
# Drop unwanted columns 
```

##### Step 3: Daily Summary

```{r}
# Summarize by day
## Need to set first difference values to 0
pondflux_daily <- pondflux_15min %>%
  group_by(Date) %>% 
  summarize(WSEmin = min(WSE), WSEmean = mean(WSE),WSEmax = max(WSE),precip_event_mm = sum(precip_event_mm), precip_acc_mm = max(precip_acc_mm), VOLmin =min(VOLacft), VOLmean = mean(VOLacft), VOLmax = max(VOLacft), SAmin = min(SAac), SAmean = mean(SAac), SAmax = max(SAac), PCPacft = sum(PCPacft)) %>% 
  mutate(VOLchg = c(VOLmax[1], diff(VOLmax)),VOLchg = if_else(VOLchg == VOLmax, 0, VOLchg), SAchg = c(SAmax[1], diff(SAmax)), SAchg = if_else(SAmax == SAchg, 0, SAchg), AcPerDay = (VOLchg/SAmax)) #%>% 
#  write.csv("output/pondflux_daily.csv")
  
# Max WSE 

```

#### Step 4: ET Rate
```{r}
plot(pondflux_daily$Date, pondflux_daily$VOLchg)+
  abline(lm(pondflux_daily$VOLchg~pondflux_daily$Date), col="red")

mean_test <- mean(pondflux_daily$VOLchg)
mean_test
median_test <- median(pondflux_daily$VOLchg)
median_test
summary_stats <- summary(pondflux_daily$VOLchg)
summary_stats

ETtest <- lm(pondflux_daily$VOLchg~pondflux_daily$Date)
ETtest
```

#Filter March and April Storms
```{r}
march.storm <- filter(pondflux_15min, Date >= "2018-03-20" & Date <="2018-03-22") %>% 
  mutate(Event_Acc = cumsum(precip_event_mm), VOLgain = VOLacft-8.571884, PCPacft_acc = cumsum(PCPacft))

april.storm <- filter(pondflux_15min, Date >= "2018-04-06" & Date <="2018-04-07") %>% 
  mutate(Event_Acc = cumsum(precip_event_mm), VOLgain = VOLacft-20.18068, PCPacft_acc = cumsum(PCPacft))

```

#Plot March Storm Hyetograph
```{r}
#png("figs/march_storm_hyetograph.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
plot(march.storm$DateTime, march.storm$precip_event_mm, type = "h", ylab = "Precipitation Event (mm)", main = "March Storm Hyetograph", xlab = "March 20-22, 2018", col = "deepskyblue")
par(new = TRUE)
plot(march.storm$DateTime, march.storm$Event_Acc, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Accumulated Precipitation (mm)", side = 4, line = 3)
legend("topleft", c("Event", "Accumulated"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```
#Plot March Storm Pond Fill
```{r}
#png("figs/march_storm_pondfill.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
plot(march.storm$DateTime, march.storm$precip_event_mm, type = "h", ylab = "Precipitation (mm)", main = "March Storm Pond Fill", xlab = "March 20-22, 2018", col = "deepskyblue")
par(new = TRUE)
plot(march.storm$DateTime, despike(march.storm$VOLgain, reference="median", n = 1, k = 31), type = "l", xaxt = "n", yaxt = "n", ylab = "n", xlab = "n", col = "darkblue", lty = 3)
axis(side = 4)
mtext("Accumulated Volume (ac-ft)", side = 4, line = 3)
legend("topleft", c("Precip Event", "Pond Voume"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```
#Plot March Storm Pond Fill
```{r}
#png("figs/march_storm_pondfill.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
plot(march.storm$DateTime, march.storm$precip_event_mm, type = "h", ylab = "Precipitation (mm)", main = "March Storm Pond Fill", xlab = "March 20-22, 2018", col = "deepskyblue")
par(new = TRUE)
plot(march.storm$DateTime, despike(march.storm$VOLgain, reference="median", n = 1, k = 31), type = "l", xaxt = "n", yaxt = "n", ylab = "n", xlab = "n", col = "darkblue", lty = 3)
axis(side = 4)
mtext("Accumulated Volume (ac-ft)", side = 4, line = 3)
legend("topleft", c("Precip Event", "Pond Voume"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```
#Plot March Storm Pond Volume Gain vs. Precip Volume
```{r}
#png("figs/march_storm_pondprecip_vol.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
 plot(march.storm$DateTime, march.storm$PCPacft_acc, type = "l", yaxt = "n", ylab = "", main = "March Storm Precip vs. Pond Volume", xlab = "March 20-22, 2018", col = "deepskyblue")
 axis(side = 4)
 lines(march.storm$DateTime, despike(march.storm$VOLgain, reference="median", n = 1, k = 31), type = "l", xaxt = "n", yaxt = "n", ylab = "n", xlab = "n", col = "darkblue", lty = 3)
mtext("Accumulated Volume (ac-ft)", side = 4, line = 3)
 legend("topleft", c("Precip Volume", "Pond Voume"),
        col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```

#Filter April Storm Hyetograph
```{r}
#png("figs/april_storm_hyetograph.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
plot(april.storm$DateTime, april.storm$precip_event_mm, type = "h", ylab = "Precipitation Event (mm)", main = "April Storm Hyetograph", xlab = "April 6-7, 2018", col = "deepskyblue")
par(new = TRUE)
plot(april.storm$DateTime, april.storm$Event_Acc, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Accumulated Precipitation (mm)", side = 4, line = 3)
legend("topleft", c("Event", "Accumulated"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```

#Plot April Storm Pond Fill
```{r}
#png("figs/april_storm_pondfill.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
plot(april.storm$DateTime, april.storm$precip_event_mm, type = "h", ylab = "Precipitation (mm)", main = "April Storm Pond Fill", xlab = "April 6-7, 2018", col = "deepskyblue")
par(new = TRUE)
plot(april.storm$DateTime, despike(april.storm$VOLgain, reference="median", n = 1, k = 31), type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 3)
axis(side = 4)
mtext("Accumulated Volume (ac-ft)", side = 4, line = 3)
legend("topleft", c("Precip Event", "Pond Voume"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 3))
#dev.off()
```
#Plot April Storm Pond Volume Gain vs. Precip Volume
```{r}
#png("figs/april_storm_pondprecip_vol.png", width = 600, height = 400)
par(mar = c(5, 5, 3, 5))
 plot(april.storm$DateTime, april.storm$PCPacft_acc, type = "l", yaxt = "n", ylab = "", main = "April Storm Precip vs. Pond Volume", xlab = "April 6-7, 2018", col = "deepskyblue")
 axis(side = 4)
 lines(april.storm$DateTime, despike(april.storm$VOLgain, reference="median", n = 1, k = 31), type = "l", xaxt = "n", yaxt = "n", ylab = "n", xlab = "n", col = "darkblue", lty = 3)
mtext("Accumulated Volume (ac-ft)", side = 4, line = 3)
 legend("topleft", c("Precip Volume", "Pond Voume"),
        col = c("deepskyblue", "darkblue"), lty = c(1, 2))
#dev.off()
```

#Plot Seasonal Pond Volume against Precipitation Events 
```{r}
#png("figs/season_filldrawdown.png", width = 600, height = 400)

par(mar = c(5, 5, 3, 5))
plot(pondflux_daily$Date, pondflux_daily$precip_event_mm, type = "h", ylab = "Precipitation (mm)", main = "Pond Fill and Drawdown", xlab = "November 6, 2017 - July 23, 2018", col = "deepskyblue", lty = 1)
par(new = TRUE)
plot(pondflux_daily$Date, pondflux_daily$VOLmean, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Volume (ac-ft)", side = 4, line = 3)
legend("topleft", c("Precip Event","Pond Volume"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

#dev.off()

```
#Plot Seasonal Pond Volume against Accumulated Precipitation 
```{r}
#png("figs/season_filldrawdown_acc.png", width = 600, height = 400)

par(mar = c(5, 5, 3, 5))
plot(pondflux_daily$Date, pondflux_daily$precip_acc_mm, type = "l", ylab = "Accumulated Precipitation (mm)", main = "Pond Fill and Drawdown", xlab = "November 6, 2017 - July 23, 2018", col = "deepskyblue", lty = 1)
par(new = TRUE)
plot(pondflux_daily$Date, pondflux_daily$VOLmean, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Volume (ac-ft)", side = 4, line = 3)
legend("topleft", c("Acc Precip","Pond Volume"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

#dev.off()

```

#Plot Precipitation Events Against Accumulated Precipitation
```{r}
#png("figs/season_precipitation.png", width = 600, height = 400)

par(mar = c(5, 5, 3, 5))
plot(pondflux_daily$Date, pondflux_daily$precip_event_mm, type = "h", ylab = "Precipitation Event (mm)", main = "Precipitation", xlab = "November 6, 2017 - July 23, 2018", col = "deepskyblue")
par(new = TRUE)
plot(pondflux_daily$Date, pondflux_daily$precip_acc_mm, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Accumulated Precipitation (mm)", side = 4, line = 3)
legend("topleft", c("Event", "Accumulated"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

#dev.off()

```

#Attempt to combine figures into single stacked, SQUASHED
```{r}
# attach(daily_test)
# par(mfrow=c(2,1))
# 
# par(mar = c(5, 5, 3, 5))
# plot(daily_test$Date, daily_test$VOLmean, type = "l", ylab = "Volume (ac-ft)", main = "Pond Volume vs. Precipitation Events", xlab = "Date", col = "darkblue", lty = 2)
# par(new = TRUE)
# plot(daily_test$Date, daily_test$precip_event_mm, type = "h", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "deepskyblue")
# axis(side = 4)
# mtext("Precip (mm)", side = 4, line = 3)
# legend("topleft", c("Vol (ac-ft)", "Precip (mm)"),
#        col = c("darkblue", "deepskyblue"), lty = c(2, 1))
# 
# par(mar = c(5, 5, 3, 5))
# plot(daily_test$Date, daily_test$precip_event_mm, type = "h", ylab = "Precip (mm)", main = "Precipitation Events vs. Accumulated Precipitation", xlab = "Date", col = "deepskyblue")
# par(new = TRUE)
# plot(daily_test$Date, daily_test$precip_acc_mm, type = "l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
# axis(side = 4)
# mtext("Precip (mm)", side = 4, line = 3)
# legend("topleft", c("Precip Event (mm)", "Acc Precip (mm)"),
#        col = c("deepskyblue", "darkblue"), lty = c(1, 2))
```

##### Write out to CSV
Last version written on: oct. 6th 2018 

```{r}

```

