---
title: "AVO_Precip_WSE"
output: html_notebook
---

Load required packages
```{r}
#library(plyr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(rvest)
library(readr)
library(grid)
#library(sharpshootR)
#library(gplots)
library(CDECRetrieve)
```
Load Precip data 
```{r}
#x <- read_csv("data/AVO_CDECprecip_1718.csv")

x <- cdec_query("ucm", 2, dur_code = "E", start_date = "2017-11-06", end_date = "2018-07-23")

#Edit columns
#x$DateTime <- as.POSIXct(x$ACTUAL_DATE)

#Calculate event data from accumulated data 
#Create lag 
x$lag <- lag(x$parameter_value, k = 1)

#Difference to get precip events in cm 
x$precip_event_cm <- (x$parameter_value-x$lag)*2.54

#Convert accumulated precip to cm
x$precip_acc_cm <- (x$parameter_value)*2.54

#Change column name
names(x)[3]<-"DateTime"

```


Load Processed Inflow Data
```{r}
inflow <- read_csv("data/AVO_Inflows_15min.csv")
```
Join Inflow and Precip Data
```{r}
y <- inner_join(inflow, x, by = "DateTime")

#Create columns for depth in different units
y$Depth_m <- (y$WSE-120.77)
y$Depth_cm <- (y$WSE-120.77)*100

#Calculate day to day % change in precip

# Percent Change for Precip
#https://stackoverflow.com/questions/48196552/calculate-percentage-change-in-r-using-dplyr 
##DOUBLE CHECK IF LAG FUNCTION IS CORRECT##
y$precip_pct_chg <- (y$precip_acc_cm/lag(y$precip_acc_cm, k = -1)-1) * 100
# Percent of Total
y$precip_pct_tot <- (y$precip_acc_cm/25.5778) * 100

#Percent Change for Pond
y$depth_pct_chg <- (y$Depth_m/lag(y$Depth_m, k = -1) - 1) * 100
#Remove negative values - only interested in gains
y$depth_pct_chg <- if_else(y$depth_pct_chg<0, 0, y$depth_pct_chg)



# Percent of Total (maximum???)
y$depth_pct_tot <- (y$Depth_m/(124.14-120.77)) * 100

#Add Month column for grouping 
y$Month <- month(y$DateTime)
y$Day <- day(y$DateTime)
y$Year <- year(y$DateTime)
y$Date <- date(y$DateTime)
y$Time <- format(ymd_hms(y$DateTime), "%H:%M:%S")

```


Plot Cumulative Precip and Depth (Base R)
```{r}
# https://thepracticalr.wordpress.com/2016/08/30/2-y-axis-plotting/ 

png("figs/depth_precip_cum.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(y$DateTime, y$Depth_cm, type ="l", ylab = "Depth (cm)", main = "Depth vs. Cumulative Precip", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(y$DateTime, y$precip_acc_cm, type ="l", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Precip (cm)", side = 4, line = 3)
legend("topleft", c("Depth (cm)", "Precip (cm)"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

dev.off()
```
Plot Cumulative Annual Precip and Depth (ggplot)
```{r}
p <- ggplot(y, aes(x = DateTime))
  p <- p + geom_line(aes(y = Depth_cm), lty = 1, col = "deepskyblue") #+ coord_cartesian(ylim=c(120, 125))

  # adding the precip, transformed to match roughly the range of the WSE
  p <- p + geom_line(aes(y = precip_acc_cm*7), lty = 3, col = "darkblue")
  p

  # now adding the secondary axis, following the example in the help file ?scale_y_continuous
  # and, very important, reverting the above transformation
  p <- p + scale_y_continuous(sec.axis = sec_axis(~./7, name = "Precipitation (cm)"))

  # modifying colours and theme options
  #p <- p + scale_colour_manual(labels = c("Water Surface Elevation (cm)", "Precipitation (cm)"), values = c("blue","red"))
  p <- p + labs(y = "Depth (cm)",
                x = "Date",
                colour = NULL)
  p <- p + ggtitle("Depth vs. Cumulative Precip")
  p <- p + theme(plot.title = element_text(hjust = 0.5))
  p  <- p + theme(legend.position = c(0.85, 0.85))
  p
  
  ggsave("figs/depth_precip_cum_ggplot.png")
```
Plot Cumulative Monthly Precip and Depth (ggplot)
```{r}
p <- ggplot(y, aes(x = Day))
  p <- p + geom_line(aes(y = Depth_cm), lty = 1, col = "deepskyblue") #+ coord_cartesian(ylim=c(120, 125))

  # adding the precip, transformed to match roughly the range of the WSE
  p <- p + geom_line(aes(y = precip_acc_cm*7), lty = 3, col = "darkblue")
  p

  # now adding the secondary axis, following the example in the help file ?scale_y_continuous
  # and, very important, reverting the above transformation
  p <- p + scale_y_continuous(sec.axis = sec_axis(~./7, name = "Precipitation (cm)"))

  # modifying colours and theme options
  #p <- p + scale_colour_manual(labels = c("Water Surface Elevation (cm)", "Precipitation (cm)"), values = c("blue","red"))
  p <- p + labs(y = "Depth (cm)",
                x = "Date",
                colour = NULL)
  p <- p + ggtitle("Monthly Depth vs. Cumulative Precip")
  p <- p + theme(plot.title = element_text(hjust = 0.5))
  p  <- p + theme(legend.position = c(0.85, 0.85))
  p <- p + facet_wrap(vars(Year, Month))
  p
  
  ggsave("figs/depth_precip_cum_monthly_ggplot.png")
```




Plot Precip vs Depth Percent Change

```{r}
#Need to sort out noise in data - aggregate to daily? Only positive values for WSE

png("figs/depth_precip_pctchange.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(y$DateTime, y$precip_pct_chg, type ="l", ylab = "% Change in Precip", main = "%Change Precip vs. Depth", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(y$DateTime, y$depth_pct_chg, type ="p", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("% Change in Depth", side = 4, line = 3)
legend("topright", c("% Change in Precip", "% Change in Depth"),
       col = c("deepskyblue", "darkblue"), lty = c(1, 2))

dev.off()
```


Stacked WSE and Precip
```{r}
# p1 <- ggplot(y, aes(x = DateTime))
#   p1 <- p1 + geom_line(aes(y = WSE), lty = 1) 
#   p1
#   
# p2 <- ggplot(y, aes(x = DateTime))
#   p2 <- p2 + geom_line(aes(y = precip_cm), lty = 1) 
#   p2
# 
# grid.newpage()
# ggsave("wse_precip.jpg", path = "E:/AVOCET/AVOCET_GIT/figs", plot = grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), size = "last")))
```


Filtering for Storm Events by Threshold and Assigning Event Codes
```{r}

#Create threshold to find days with precip events
threshold <- y %>% 
  filter(precip_event_cm > 0.0) %>%
  group_by(Date) %>%
  mutate(count = n())

#Create vector of unique dates to identify storm events 
storm_days <- unique(threshold$Date)
storm_days <- as_tibble(storm_days)
names(storm_days)[1] <- "Date"

#filter pond data to storm events
pond_storms <- semi_join(y, storm_days, by = "Date")
# Create Storm Event Groupings based on consecutive days https://stackoverflow.com/questions/37342412/r-find-dates-consecutive 
pond_storms$storm_event <- cumsum(c(1, diff.Date(pond_storms$Date)) >= 2)
pond_storms

write.csv(pond_storms, file = "output/pond_storms.csv")

 storm_stats <- pond_storms %>% 
  group_by(storm_event) %>% 
  summarise(precip_mm = (max(precip_acc_cm)-min(precip_acc_cm))*10, vol_gain = (max(VOLUME)-min(VOLUME)), start_date = min(Date), end_date = max(Date))
 
 storm_stats$duration <- paste(storm_stats$start_date, storm_stats$end_date, sep = "-")
 write.csv(storm_stats, file = "output/storm_stats.csv")
```


Plotting Storm Event Precip by Pond Vol Gain
```{r}
# ps <- plot(storm_stats$precip_mm, storm_stats$vol_gain, ylab = "Pond Volume Gain m^3", main = "Storm Events vs. Pond Volume", xlab = "Precip (mm)", col = as.factor(storm_stats$duration))
# legend("topleft", unique(storm_stats$duration),
#        col = as.factor(storm_stats$duration))
# 
# ps <- plot(storm_stats$precip_mm, storm_stats$vol_gain, ylab = "Pond Volume Gain m^3", main = "Storm Events vs. Pond Volume", xlab = "Precip (mm)", col = as.factor(storm_stats$storm_event))
# legend("topleft", legend = as.factor(storm_stats$storm_event), col=1:length(storm_stats$storm_event), pch = storm_stats$storm_event, ncol = 3)


```
Plotting Storm Event Precip and Pond Vol Gain
```{r}
#storms <- plot(storm_stats$start_date, storm_stats$vol_gain, ylab = "Pond Volume Gain m^3", main = "Storm Events vs. Pond Volume", xlab = "Date")
#precip <- plot(storm_stats$start_date, storm_stats$precip_mm, ylab = "Precip (mm)", main = "Storm Events vs. Pond Volume", xlab = "Date")

png("figs/storms_vol_precip.png", width = 800, height = 600)

par(mar = c(5, 5, 3, 5))
plot(storm_stats$start_date, storm_stats$vol_gain, type ="p", pch = 19, ylab = "Volume (m^3)", main = "Storm Events vs. Pond Volume", xlab = "Date", col = "deepskyblue")
par(new = TRUE)
plot(storm_stats$start_date, storm_stats$precip_mm, type ="p", xaxt = "n", yaxt = "n", ylab = "", xlab = "", col = "darkblue", lty = 2)
axis(side = 4)
mtext("Precip (mm)", side = 4, line = 3)
legend("left", inset = 0.01, c("Volume (m^3)", "Precip (mm)"),
       col = c("deepskyblue", "darkblue"), pch = c(19, 1))

dev.off()
```

Determine Catchment Area Draining into AVO
```{r}
PHE_subbasins <- read_csv("data/PHE_subbasins.csv") 
pond_subs <- PHE_subbasins[c(-2,-5,-6,-7),]
AVO_catch <- sum(pond_subs$Shape_Area)
AVO_catch
  
```

Plot precip per day (depth mm x area of catchments) x vol of pond per day for each storm event
```{r}
storm_stats$precip_vol <- storm_stats$precip_mm*0.001*AVO_catch


```

```{r}
test <- pond_storms %>% 
  group_by(storm_event) %>% 
  summarise(start_date = first(DateTime), end_date = last(DateTime))
```


Parse Out Storm Event Tables
```{r}
#https://stackoverflow.com/questions/13629659/efficient-way-to-output-subset-of-data-frame-based-on-column
# http://rprogramming.net/write-csv-in-r/
## Need to figure out how to write to output folder
storm_tables <- function(storm_event) {
  write.csv(pond_storms[pond_storms$storm_event == storm_event, ]
              , file = paste0("storm_event_", storm_event, ".csv")
              )
}

lapply(unique(pond_storms$storm_event), storm_tables)

```


